Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-21 experiments.tex
minor changes

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensive, resulting in runtimes that are two orders of
magnitudes larger than without calibration. Strikingly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

@@

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  3811ms& 84.4 / 83.0           & 12.4 sec\\
    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
    WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
    \hline
  \end{tabular}
  \caption{Average Precision(AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and runtime for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}

>>>>

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensive, resulting in generation time that are two orders of
magnitudes larger than without calibration. Strikingly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

@@

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  6162ms& 84.4 / 83.0           & 15.4 sec\\
    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
    WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
    \hline
  \end{tabular}
  \caption{Average Precision(AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}
